Toward Supervised Reinforcement Learning with Partial States for Social HRI

### 2017-08-29 paper.tex
Typos

When environments do not supply rewards, they can be replaced by human ones. For
example, the TAMER framework~\cite{knox2009interactively} derives a reward
function from the human feedbacks and uses this function to evaluate the current
behaviour. In a similar approach, MacGlashan et al. proposed COACH
in~\cite{macglashan2017interactive}. COACH assumes that human rewards represent
the advantage function, i.e. how much the current action is better than the
current policy, allowing to adapt the reward function to the strategies used and
the current state of the learner.

@@

Compared to similar algorithms
\cite{chernova2009interactive,walsh2010generalizing}, which allows the agent to
request demonstrations and/or the teacher to provide demonstrations to correct
mistakes made by the robot, SPARC allows the teacher to correct any action
before its execution, thus reducing importantly the risk of the agent making
errors. The total blending between autonomous execution of actions and
demonstrations and the control over \emph{every} actions executed by the agent
are the specificities of SPARC.

@@

\begin{algorithm}
    \DontPrintSemicolon
    \SetKwInOut{Input}{inputs}\SetKwInOut{Output}{output}
    \Input{Current state $s$, set of  $(a,s',r)$}
    \Output{selected action $\pi(s)$}
    \ForEach{$a \in \mathcal{A}$}{
        \ForEach{$p=(s',r) \in \mathcal{C}_{a}$}{
            compute similarity $\Delta$ between $s$ and $s'$:
            $\Delta(p)=1-\frac{\sum_{i}^{n'}(s'(i)-s(i))^{2}}{n'}$
        }
        find closest pair $\hat{p}$:\\
        $\hat{p} = arg\, max_{p} \Delta(p)$\\
        compute expected reward $\hat{r}(a)$ for taking $a$ in $s$:\\
        $\hat{r}(a) = \Delta (\hat{p}) \cdot r(\hat{p})$\\
        with $r(p)$ the reward of $p = (s',r)$ 
    }
    Select the action with the maximum expected reward:
    $\pi(s) = arg\, max_{a} \hat{r}(a)$

>>>>

When environments do not supply rewards, they can be replaced by human ones. For
example, the TAMER framework~\cite{knox2009interactively} derives a reward
function from the human feedback and uses this function to evaluate the current
behaviour. In a similar approach, MacGlashan et al. proposed COACH
in~\cite{macglashan2017interactive}. COACH assumes that human rewards represent
the advantage function, i.e. how much the current action is better than the
current policy, allowing to adapt the reward function to the strategies used and
the current state of the learner.

@@

Compared to similar algorithms
\cite{chernova2009interactive,walsh2010generalizing}, which allow the agent to
request demonstrations and/or the teacher to provide demonstrations to correct
mistakes made by the robot, SPARC allows the teacher to correct any action
before its execution, thus reducing importantly the risk of the agent making
errors. The total blending between autonomous execution of actions and
demonstrations and the control over \emph{every} actions executed by the agent
are the specificities of SPARC.

@@

\begin{algorithm}
    \DontPrintSemicolon
    \SetKwInOut{Input}{inputs}\SetKwInOut{Output}{output}
    \Input{Current state $s$, set of  $(a,s',r)$}
    \Output{selected action $\pi(s)$}
    \ForEach{$a \in \mathcal{A}$}{
        \ForEach{$p=(s',r) \in \mathcal{C}_{a}$}{
            compute similarity $\Delta$ between $s$ and $s'$:
            $\Delta(p)=1-\frac{\sum_{i}^{n'}(s'(i)-s(i))^{2}}{n'}$
        }
        find closest pair $\hat{p}$:\\
        $\hat{p} = arg\, max_{p} \Delta(p)$\\
        compute expected reward $\hat{r}(a)$ for taking $a$ in $s$:\\
        $\hat{r}(a) = \Delta (\hat{p}) \cdot r(\hat{p})$\\
        with $r(p)$ the reward $r$ of the pair $p = (s',r)$ 
    }
    Select the action with the maximum expected reward:
    $\pi(s) = arg\, max_{a} \hat{r}(a)$
